Generation of TypeScript Declaration Files from JavaScript Code

### 2021-05-18 mplr-2021/main.tex
reviewer#1

The generated declaration file shown in \figref{fig:motivating-example-glob-to-regexp-vscode}
describes a package with a single exported function. The module name
is derived from the NPM module name by camlization\footnote{i.e.,
  transforming to camel case.}. The first parameter is of type
\texttt{string} and the second one is an optional object described by
an interface. To avoid name clashes, \texttt{dts-generate} creates a
namespace that corresponds to the module name. This pattern is a best
practice to  organize types declared in a declaration file
\cite{typescript-namespaces}. In the example, the interface
\lstinline[language=TypeScript]{I__opts} is declared in namespace
\lstinline[language=TypeScript]{globToRegexp}. Hence, its uses
must be qualified by the namespace as in
\lstinline[language=TypeScript]{globToRegexp.I__opts}. The name of the
interface is derived from the name of the formal parameter.

@@

\item Extract the code examples from the README file. To this end,
  observe that README files are
  written using Markdown\footnote{\url{https://www.markdownguide.org}}, a
  popular markup language, where
  code examples are presented in code blocks labeled with the programming
  language, so that syntax highlighting is done correctly. Hence, we
  retrieve the code examples from code blocks labeled \texttt{js} or
  \texttt{javascript}, which both stand for JavaScript in
  Markdown.
\end{itemize}

@@

\paragraph*{Extraction of Code Examples}
In this step, we loose another 50\% of modules! This loss is mainly
explained because some developers do not wrap their code in a block
using the \texttt{javascript} or \texttt{js} tags. As we are
still left with code examples for \CountModulesWithCodeExamples{} modules, we did not look
further into code extraction as this number was considered sufficient for
evaluating the generation of declaration files.

>>>>

The generated declaration file shown in \figref{fig:motivating-example-glob-to-regexp-vscode}
describes a package with a single exported function. The module name
is derived from the NPM module name by camlization\footnote{i.e.,
  transforming to camel case.}. The first parameter is of type
\texttt{string} and the second one is an optional object described by
an interface. To avoid name clashes, \texttt{dts-generate} creates a
namespace that corresponds to the module name. This pattern is a best
practice to  organize types declared in a declaration file
\cite{typescript-namespaces}. In the example, the interface
\lstinline[language=TypeScript]{I__opts} is declared in namespace
\lstinline[language=TypeScript]{GlobToRegexp}. Hence, its uses
must be qualified by the namespace as in
\lstinline[language=TypeScript]{GlobToRegexp.I__opts}. The name of the
interface is derived from the name of the formal parameter.

@@

\item Extract the code examples from the README file. To this end,
  observe that README files are
  written using Markdown\footnote{\url{https://www.markdownguide.org}}, a
  popular markup language, where
  code examples are presented in code blocks labeled with the programming
  language. Hence, we
  retrieve the code examples from code blocks labeled \texttt{js} or
  \texttt{javascript}, which both stand for JavaScript in
  Markdown.
\end{itemize}

@@

\paragraph*{Extraction of Code Examples}
In this step, we lose another 50\% of modules! This loss is mainly
explained because some developers do not wrap their code in a block
using the \texttt{javascript} or \texttt{js} tags. As we are
still left with code examples for \CountModulesWithCodeExamples{} modules, we did not look
further into code extraction as this number was considered sufficient for
evaluating the generation of declaration files.
